---
title: "Untitled"
author: "Mizza"
date: "2024-06-24"
output: html_document
---

```{r}
#| label: setup
#| warning: false
#| echo: false

library(ggplot2)
library(readxl)
library(dplyr)
library(tidyverse)
library(tidyr)
library(survey)
library(ggsankey)

Household <- read_excel("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/2_LASI_W1_Household_v4 1.xlsx")
Individual <- read_excel("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/3_LASI_W1_Individual_data 1.xlsx")
merged_data <- merge (Individual, Household, by = "hhid", all = TRUE)
roster <- read_excel ("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/1_LASI_W1_HH_roster 1.xlsx")
final_data <- merge (merged_data, roster, by = "hhid", all = TRUE)
```


**DATA OF VULNERABLE GROUP - SENIOR CITIZENS**

```{r}
final_data <- final_data%>%
  rename(Age = dm005)
```

```{r}

##TO APPLY AGE FILTER##
create_age_category <- function(Age) {
  if (is.na(Age)) {
    return(NA)
  }
  
  if (Age >= 60 & Age <= 69) {
    return("Young Old")
  } else if (Age >= 70 & Age <= 79) {
    return("Old")
  } else if (Age >= 80) {
    return("Very Old")
  } else {
    return(NA) 
  }
}
final_data$AgeCategory <- sapply(final_data$Age, create_age_category)

final_data <- final_data[final_data$AgeCategory %in% c("Young Old", "Old", "Very Old"), ]
```


**EDUCATION BUCKET**

```{r}
final_data <- final_data %>%
  mutate(Education_level = case_when(
    dm006 == "2 No" ~ "Uneducated",
    dm008 %in% c("1 Less than Primary (Standard 1-4)", 
                 "2 Primary Completed (Standard 5-7)", 
                 "3 Middle Completed (Standard 8- 9)") ~ "Primary School",
    dm008 == "4 Secondary School/Matriculation completed" ~ "Secondary School",
    dm008 %in% c("5 Higher Secondary/Intermediate/Senior Secondary completed", 
                 "6 Diploma and certificate holders") ~ "Senior Secondary School",
    dm008 %in% c("7 Graduate degree (B.A., B.Sc., B. Com.) completed", 
                 "8 Post-graduate degree or (M.A., M.Sc., M. Com.) above (M.Phil, Ph.D., Post-Doc) completed", 
                 "9 Professional course/degree (B.Ed, BE, B.Tech, MBBS, BHMS, BAMS, B.Pharm, BCS, BCA, BBA, LLB, BVSc., B. Arch, M.Ed, ME, M.Tech, MD, M.Pharm, MCS, MCA, MBA,LLM, MVSc., M. Arch, MS, CA, CS, CWA)Completed") ~ "Tertiary Education",
    TRUE ~ "Other"
  ))
```

```{r}
final_data<- final_data%>%
  rename(Gender = dm003)
```

```{r}
male<- final_data%>%
  filter(Gender == "1 Male")
```

```{r}
female<- final_data%>%
  filter(Gender == "2 Female")
```


**_____INTENTION TO CHANGE_____**

```{r}
male <- male %>%
  rename(Intention_change = fs331)
```


*General Analysis*

*(i) Male*
```{r}
# Create a copy of the dataset to avoid modifying the original data
male$change <- male$Intention_change

# Define the values to be replaced with "Yes"
values_to_replace <- c(
  "2 Yes, prefer to live alone",
  "3 Yes, prefer to live with spouse only",
  "4 Yes, prefer to live with other child",
  "5 Yes, prefer to live with other relatives",
  "6 Yes, prefer to live with my own family (spouse and children) only",
  "7 Yes, prefer to move into old age home"
)

# Replace the specified values with "Yes" in the "change" column
male$change[male$Intention_change %in% values_to_replace] <- "Yes"


# Create the frequency distribution table
frequency2 <- table(male$change)
print(frequency2)

# Proportion table
proportion_table2 <- prop.table(frequency2) * 100  
print(round(proportion_table, digits=2))

# Define the survey design
design2 <- svydesign(id = ~1, weights = ~stateindividualweight, data = male)

# Create a weighted frequency distribution table
svytable_design2 <- svytable(~change, design = design2)
print(svytable_design2)

# Proportion table from the weighted frequency distribution
weighted_proportion_table2 <- prop.table(svytable_design2) * 100  
print(round(weighted_proportion_table2, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df2 <- as.data.frame(weighted_proportion_table2)
```



*(ii) Female*
```{r}
female <- female %>%
  rename(Intention_change = fs331)
```

```{r}
# Create a copy of the dataset to avoid modifying the original data
female$change <- female$Intention_change

# Define the values to be replaced with "Yes"
values_to_replace <- c(
  "2 Yes, prefer to live alone",
  "3 Yes, prefer to live with spouse only",
  "4 Yes, prefer to live with other child",
  "5 Yes, prefer to live with other relatives",
  "6 Yes, prefer to live with my own family (spouse and children) only",
  "7 Yes, prefer to move into old age home"
)

# Replace the specified values with "Yes" in the "change" column
female$change[female$Intention_change %in% values_to_replace] <- "Yes"


# Create the frequency distribution table
frequency2a <- table(female$change)
print(frequency2a)

# Define the survey design
design2a <- svydesign(id = ~1, weights = ~stateindividualweight, data = female)

# Create a weighted frequency distribution table
svytable_design2a <- svytable(~change, design = design2a)
print(svytable_design2a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table2a <- prop.table(svytable_design2a) * 100  
print(round(weighted_proportion_table2a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df2a <- as.data.frame(weighted_proportion_table2a)
```


**I. Satisfaction**

```{r}
male<- male%>%
  rename(Satisfaction= fs329)
```


*(i) Male*
```{r}
# Create the frequency distribution table
frequency3 <- table(male$Satisfaction)
print(frequency3)

# Proportion table
proportion_table3 <- prop.table(frequency3) * 100  
print(round(proportion_table3, digits=2))

# Define the survey design
design3 <- svydesign(id = ~1, weights = ~stateindividualweight, data = male)

# Create a weighted frequency distribution table
svytable_design3 <- svytable(~Satisfaction, design = design3)
print(svytable_design3)

# Proportion table from the weighted frequency distribution
weighted_proportion_table3<- prop.table(svytable_design3) * 100  
print(round(weighted_proportion_table3, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df3 <- as.data.frame(weighted_proportion_table3)
```


*(ii) Female*
```{r}
female<- female%>%
  rename(Satisfaction= fs329)
```

```{r}
# Create the frequency distribution table
frequency3z <- table(female$Satisfaction)
print(frequency3z)

# Proportion table
proportion_table3z <- prop.table(frequency3) * 100  
print(round(proportion_table3z, digits=2))

# Define the survey design
design3z <- svydesign(id = ~1, weights = ~stateindividualweight, data = female)

# Create a weighted frequency distribution table
svytable_design3z <- svytable(~Satisfaction, design = design3z)
print(svytable_design3z)

# Proportion table from the weighted frequency distribution
weighted_proportion_table3z<- prop.table(svytable_design3z) * 100  
print(round(weighted_proportion_table3z, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df3z <- as.data.frame(weighted_proportion_table3z)
```



**II. Decision making**

*(i) Male*

```{r}
male<- male%>%
  rename(Decision = fs330)
```

```{r}
# Create a copy of the dataset to avoid modifying the original data
male$Decision <- male$Decision

# Define the values to be replaced with "family"
values_to_replace <- c(
  "10 Daughter-in-law",
  "12 Grand parents",
  "13 Parent-in-law",
  "14 Other relatives",
  "2 Father",
  "3 Mother",
  "4 Brother/s",
  "5 Sister/s",
  "6 Spouse / partner",
  "7 Son/s",
  "8 Daughter/s",
  "9 Son-in-law"
)

# Replace the specified values with "Yes" in the "change" column
male$Decision[male$Decision %in% values_to_replace] <- "family"


# Create the frequency distribution table
frequency4a <- table(male$Decision)
print(frequency4a)

# Define the survey design
design4a <- svydesign(id = ~1, weights = ~stateindividualweight, data = male)

# Create a weighted frequency distribution table
svytable_design4a <- svytable(~Decision, design = design4a)
print(svytable_design4a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4a <- prop.table(svytable_design4a) * 100  
print(round(weighted_proportion_table4a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4a <- as.data.frame(weighted_proportion_table4a)
```


*(ii) Female*

```{r}
female<- female%>%
  rename(Decision = fs330)
```

```{r}
# Create a copy of the dataset to avoid modifying the original data
female$Decision <- female$Decision

# Define the values to be replaced with "family"
values_to_replace <- c(
  "10 Daughter-in-law",
  "12 Grand parents",
  "13 Parent-in-law",
  "14 Other relatives",
  "2 Father",
  "3 Mother",
  "4 Brother/s",
  "5 Sister/s",
  "6 Spouse / partner",
  "7 Son/s",
  "8 Daughter/s",
  "9 Son-in-law"
)

# Replace the specified values with "Yes" in the "change" column
female$Decision[female$Decision %in% values_to_replace] <- "family"


# Create the frequency distribution table
frequency4ab <- table(female$Decision)
print(frequency4ab)

# Define the survey design
design4a <- svydesign(id = ~1, weights = ~stateindividualweight, data = female)

# Create a weighted frequency distribution table
svytable_design4a <- svytable(~Decision, design = design4a)
print(svytable_design4a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4a <- prop.table(svytable_design4a) * 100  
print(round(weighted_proportion_table4a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4a <- as.data.frame(weighted_proportion_table4a)
```




**______SOCIAL RELATIONSHIP**

**I. Interaction with friends and family**

**1. Close Relationship**

*(i) Male*
```{r}
male <- male %>%
  rename(family = fs323)
```

**1. Family Relation - Yes**
```{r}
fam_relation_yesm<- male%>%
  filter(fs323s1 == "1 Yes"| fs323s2 == "1 Yes"|fs323s3 == "1 Yes"|fs323s4 == "1 Yes"|fs323s5 == "1 Yes"|fs323s6 == "1 Yes"|fs323s7 == "1 Yes"|fs323s8 == "1 Yes"|fs323s9 == "1 Yes"|fs323s10 == "1 Yes"|fs323s11 == "1 Yes"|fs323s12 == "1 Yes"|fs323s13 == "1 Yes" )
```

**2. Friends Relation - Yes**
```{r}
frnds_relation_yesm<- male%>%
  filter(fs323s14 == "1 Yes")
```

**3. Relation with nobody**
```{r}
relation_nom<- male%>%
  filter(fs323s16 == "1 Yes")
```


*Close relation with anybody*
```{r}
# Calculate the frequency of "1 Yes" in any of the specified columns
yes_freq1 <- male%>%
  filter(fs323s1 == "1 Yes"| fs323s2 == "1 Yes"|fs323s3 == "1 Yes"|fs323s4 == "1 Yes"|fs323s5 == "1 Yes"|fs323s6 == "1 Yes"|fs323s7 == "1 Yes"|fs323s8 == "1 Yes"|fs323s9 == "1 Yes"|fs323s10 == "1 Yes"|fs323s11 == "1 Yes"|fs323s12 == "1 Yes"|fs323s13 == "1 Yes"|fs323s14 == "1 Yes"|fs323s15 == "1 Yes") %>%
  summarise(freq_yes1 = n())

# Calculate the frequency of "2 No" in all of the specified columns
no_freq1 <- male%>%
  filter(fs323s16 == "1 Yes" ) %>%
  summarise(freq_no1 = n())

# Print the results
cat("Frequency '1 Yes':", yes_freq1$freq_yes1, "\n")
cat("Frequency '2 No':", no_freq1$freq_no1, "\n")

# Calculate the frequency of "1 Yes" in any of the specified columns
yes_frequency1 <- male%>%
  filter(fs323s1 == "1 Yes"| fs323s2 == "1 Yes"|fs323s3 == "1 Yes"|fs323s4 == "1 Yes"|fs323s5 == "1 Yes"|fs323s6 == "1 Yes"|fs323s7 == "1 Yes"|fs323s8 == "1 Yes"|fs323s9 == "1 Yes"|fs323s10 == "1 Yes"|fs323s11 == "1 Yes"|fs323s12 == "1 Yes"|fs323s13 == "1 Yes"|fs323s14 == "1 Yes"|fs323s15 == "1 Yes") %>%
  summarise(freq_yes1 = sum(stateindividualweight))

# Calculate the frequency of "2 No" in all of the specified columns
no_frequency1 <- male%>%
  filter(fs323s16 == "1 Yes") %>%
  summarise(freq_no1 = sum(stateindividualweight))

# Combine the frequencies and calculate the proportions
total_responses1 <- sum(male$stateindividualweight)
yes_proportion1 <- (yes_frequency1$freq_yes1 / total_responses1)*100
no_proportion1 <- (no_frequency1$freq_no1 / total_responses1)*100

# Create a data frame with the results
results1 <- data.frame(
  Response = c("1 Yes", "0 No", "NA"),
  Weighted_Proportion = c(yes_proportion1, no_proportion1, 100 - (yes_proportion1 + no_proportion1))
)

# Print the results
print(results1)
```


*(ii) Female*
```{r}
female <- female %>%
  rename(family = fs323)
```

**1. Family Relation - Yes**
```{r}
fam_relation_yesf<- female%>%
  filter(fs323s1 == "1 Yes"| fs323s2 == "1 Yes"|fs323s3 == "1 Yes"|fs323s4 == "1 Yes"|fs323s5 == "1 Yes"|fs323s6 == "1 Yes"|fs323s7 == "1 Yes"|fs323s8 == "1 Yes"|fs323s9 == "1 Yes"|fs323s10 == "1 Yes"|fs323s11 == "1 Yes"|fs323s12 == "1 Yes"|fs323s13 == "1 Yes" )
```

**2. Friends Relation - Yes**
```{r}
frnds_relation_yesf<- female%>%
  filter(fs323s14 == "1 Yes")
```

**3. Relation with nobody**
```{r}
relation_nof<- female%>%
  filter(fs323s16 == "1 Yes")
```


*Close relation with anybody*
```{r}
# Calculate the frequency of "1 Yes" in any of the specified columns
yes_freq1a <- female%>%
  filter(fs323s1 == "1 Yes"| fs323s2 == "1 Yes"|fs323s3 == "1 Yes"|fs323s4 == "1 Yes"|fs323s5 == "1 Yes"|fs323s6 == "1 Yes"|fs323s7 == "1 Yes"|fs323s8 == "1 Yes"|fs323s9 == "1 Yes"|fs323s10 == "1 Yes"|fs323s11 == "1 Yes"|fs323s12 == "1 Yes"|fs323s13 == "1 Yes"|fs323s14 == "1 Yes"|fs323s15 == "1 Yes") %>%
  summarise(freq_yes1a = n())

# Calculate the frequency of "2 No" in all of the specified columns
no_freq1a <- female%>%
  filter(fs323s16 == "1 Yes" ) %>%
  summarise(freq_no1a = n())

# Print the results
cat("Frequency '1 Yes':", yes_freq1a$freq_yes1a, "\n")
cat("Frequency '2 No':", no_freq1a$freq_no1a, "\n")

# Calculate the frequency of "1 Yes" in any of the specified columns
yes_frequency1a <- female%>%
  filter(fs323s1 == "1 Yes"| fs323s2 == "1 Yes"|fs323s3 == "1 Yes"|fs323s4 == "1 Yes"|fs323s5 == "1 Yes"|fs323s6 == "1 Yes"|fs323s7 == "1 Yes"|fs323s8 == "1 Yes"|fs323s9 == "1 Yes"|fs323s10 == "1 Yes"|fs323s11 == "1 Yes"|fs323s12 == "1 Yes"|fs323s13 == "1 Yes"|fs323s14 == "1 Yes"|fs323s15 == "1 Yes") %>%
  summarise(freq_yes1a = sum(stateindividualweight))

# Calculate the frequency of "2 No" in all of the specified columns
no_frequency1a <- female%>%
  filter(fs323s16 == "1 Yes") %>%
  summarise(freq_no1a = sum(stateindividualweight))

# Combine the frequencies and calculate the proportions
total_responses1a <- sum(female$stateindividualweight)
yes_proportion1a <- (yes_frequency1a$freq_yes1a / total_responses1a)*100
no_proportion1a <- (no_frequency1a$freq_no1a / total_responses1a)*100

# Create a data frame with the results
results1a <- data.frame(
  Response = c("1 Yes", "0 No", "NA"),
  Weighted_Proportion = c(yes_proportion1a, no_proportion1a, 100 - (yes_proportion1a + no_proportion1a))
)

# Print the results
print(results1a)
```




**2. Friends**

*(i) Male*
```{r}
male <- male %>%
  rename(friends = fs324)
```


```{r}
# Create the frequency distribution table
frequency1j <- table(male$friends)
print(frequency1j)

# Define the survey design
design1j <- svydesign(id = ~1, weights = ~stateindividualweight, data = male)

# Create a weighted frequency distribution table
svytable_design1j <- svytable(~friends, design = design1j)
print(svytable_design1j)

# Proportion table from the weighted frequency distribution
weighted_proportion_table1j <- prop.table(svytable_design1j) * 100  
print(round(weighted_proportion_table1j, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df1j <- as.data.frame(weighted_proportion_table1j)
```



**2. 1. FRIENDS - YES**

```{r}
friendsm<- male%>%
  filter(friends == "1 Yes")
```


*a. Meet up*

```{r}
# Create the frequency distribution table
frequency2j <- table(friendsm$fs326)
print(frequency2j)

# Define the survey design
design2j <- svydesign(id = ~1, weights = ~stateindividualweight, data = friendsm)

# Create a weighted frequency distribution table
svytable_design2j <- svytable(~fs326, design = design2j)
print(svytable_design2j)

# Proportion table from the weighted frequency distribution
weighted_proportion_table2j <- prop.table(svytable_design2j) * 100  
print(round(weighted_proportion_table2j, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df2j <- as.data.frame(weighted_proportion_table2j)
```


*b. e-mail/call*

```{r}
# Create the frequency distribution table
frequency3j <- table(friendsm$fs327)
print(frequency3j)

# Define the survey design
design3j <- svydesign(id = ~1, weights = ~stateindividualweight, data = friendsm)

# Create a weighted frequency distribution table
svytable_design3j <- svytable(~fs327, design = design3j)
print(svytable_design3j)

# Proportion table from the weighted frequency distribution
weighted_proportion_table3j <- prop.table(svytable_design3j) * 100  
print(round(weighted_proportion_table3j, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df3j <- as.data.frame(weighted_proportion_table3j)
```




*(ii) Female*
```{r}
female <- female %>%
  rename(friends = fs324)
```


```{r}
# Create the frequency distribution table
frequency1ja <- table(female$friends)
print(frequency1ja)

# Define the survey design
design1ja <- svydesign(id = ~1, weights = ~stateindividualweight, data = female)

# Create a weighted frequency distribution table
svytable_design1ja <- svytable(~friends, design = design1ja)
print(svytable_design1ja)

# Proportion table from the weighted frequency distribution
weighted_proportion_table1ja <- prop.table(svytable_design1ja) * 100  
print(round(weighted_proportion_table1ja, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df1ja <- as.data.frame(weighted_proportion_table1ja)
```



**2. 1. FRIENDS - YES**

```{r}
friendsf<- female%>%
  filter(friends == "1 Yes")
```


*a. Meet up*

```{r}
# Create the frequency distribution table
frequency2ja <- table(friendsf$fs326)
print(frequency2ja)

# Define the survey design
design2ja <- svydesign(id = ~1, weights = ~stateindividualweight, data = friendsf)

# Create a weighted frequency distribution table
svytable_design2ja <- svytable(~fs326, design = design2ja)
print(svytable_design2ja)

# Proportion table from the weighted frequency distribution
weighted_proportion_table2ja <- prop.table(svytable_design2ja) * 100  
print(round(weighted_proportion_table2ja, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df2ja <- as.data.frame(weighted_proportion_table2ja)
```


*b. e-mail/call*

```{r}
# Create the frequency distribution table
frequency3ja <- table(friendsf$fs327)
print(frequency3ja)

# Define the survey design
design3ja <- svydesign(id = ~1, weights = ~stateindividualweight, data = friendsf)

# Create a weighted frequency distribution table
svytable_design3ja <- svytable(~fs327, design = design3ja)
print(svytable_design3ja)

# Proportion table from the weighted frequency distribution
weighted_proportion_table3ja <- prop.table(svytable_design3ja) * 100  
print(round(weighted_proportion_table3ja, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df3ja <- as.data.frame(weighted_proportion_table3ja)
```




**II. Social Activities**


**1. Member of any Social Group**

*(i) Male*
```{r}
male<- male%>%
  rename(social_grp = fs501)
```

```{r}
# Create the frequency distribution table
frequency4j <- table(male$social_grp)
print(frequency4j)

# Define the survey design
design4j <- svydesign(id = ~1, weights = ~stateindividualweight, data = male)

# Create a weighted frequency distribution table
svytable_design4j <- svytable(~social_grp, design = design4j)
print(svytable_design4j)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4j <- prop.table(svytable_design4j) * 100  
print(round(weighted_proportion_table4j, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4j <- as.data.frame(weighted_proportion_table4j)
```



*(ii) Female*
```{r}
female<- female%>%
  rename(social_grp = fs501)
```

```{r}
# Create the frequency distribution table
frequency4ja <- table(female$social_grp)
print(frequency4ja)

# Define the survey design
design4ja <- svydesign(id = ~1, weights = ~stateindividualweight, data = female)

# Create a weighted frequency distribution table
svytable_design4ja <- svytable(~social_grp, design = design4ja)
print(svytable_design4ja)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4ja <- prop.table(svytable_design4ja) * 100  
print(round(weighted_proportion_table4ja, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4ja <- as.data.frame(weighted_proportion_table4ja)
```





**_____SOCIAL WELFARE SCHEME______**

**I. AWARENESS**

*(i) Male*

*1. Awareness - Yes*
```{r}
awarem<- male%>%
  filter(sw201a == "1 Yes" | sw201c == "1 Yes" |sw201d == "1 Yes" | sw201e == "1 Yes" )
```

*2. Awareness - No*
```{r}
unawarem<- male%>%
  filter(sw201a == "2 No" & sw201c == "2 No" & sw201d == "2 No" & sw201e == "2 No")
```


```{r}
# Calculate the frequency of "1 Yes" in any of the specified columns
yes_freq2m <- male%>%
  filter(sw201a == "1 Yes" | sw201c == "1 Yes" |sw201d == "1 Yes" | sw201e == "1 Yes") %>%
  summarise(freq_yes2m = n())

# Calculate the frequency of "2 No" in all of the specified columns
no_freq2m <- male%>%
  filter(sw201a == "2 No" & sw201c == "2 No" & sw201d == "2 No" & sw201e == "2 No") %>%
  summarise(freq_no2m = n())

# Print the results
cat("Frequency '1 Yes':", yes_freq2m$freq_yes2m, "\n")
cat("Frequency '2 No':", no_freq2m$freq_no2m, "\n")

# Calculate the frequency of "1 Yes" in any of the specified columns
yes_frequency2m <- male%>%
  filter(sw201a == "1 Yes" |sw201c == "1 Yes" |sw201d == "1 Yes") %>%
  summarise(freq_yes2m = sum(stateindividualweight))

# Calculate the frequency of "2 No" in all of the specified columns
no_frequency2m <- male%>%
  filter(sw201a == "2 No" & sw201c == "2 No" & sw201d == "2 No" ) %>%
  summarise(freq_no2m = sum(stateindividualweight))

# Combine the frequencies and calculate the proportions
total_responses2m <- sum(male$stateindividualweight)
yes_proportion2m <- (yes_frequency2m$freq_yes2m / total_responses2m)*100
no_proportion2m <- (no_frequency2m$freq_no2m / total_responses2m)*100

# Create a data frame with the results
results2m <- data.frame(
  Response = c("1 Yes", "2 No", "NA"),
  Weighted_Proportion = c(yes_proportion2m, no_proportion2m, 100 - (yes_proportion2m + no_proportion2m))
)

# Print the results
print(results2m)

```


*(ii) Female*

*1. Awareness - Yes*
```{r}
awaremf<- female%>%
  filter(sw201a == "1 Yes" | (Gender == "2 Female" & sw201b == "1 Yes") |sw201c == "1 Yes" |sw201d == "1 Yes" | sw201e == "1 Yes" )
```

*2. Awareness - No*
```{r}
unawaremf<- female%>%
  filter(sw201a == "2 No" & (Gender == "2 Female" & sw201b == "2 No") & sw201c == "2 No" & sw201d == "2 No" & sw201e == "2 No")
```


```{r}
# Calculate the frequency of "1 Yes" in any of the specified columns
yes_freq2mf <- female%>%
  filter(sw201a == "1 Yes" | (Gender == "2 Female" & sw201b == "1 Yes")  |sw201c == "1 Yes" |sw201d == "1 Yes" | sw201e == "1 Yes") %>%
  summarise(freq_yes2mf = n())

# Calculate the frequency of "2 No" in all of the specified columns
no_freq2mf <- female%>%
  filter(sw201a == "2 No" & (Gender == "2 Female" & sw201b == "2 No")  & sw201c == "2 No" & sw201d == "2 No" & sw201e == "2 No") %>%
  summarise(freq_no2mf = n())

# Print the results
cat("Frequency '1 Yes':", yes_freq2mf$freq_yes2mf, "\n")
cat("Frequency '2 No':", no_freq2mf$freq_no2mf, "\n")

# Calculate the frequency of "1 Yes" in any of the specified columns
yes_frequency2mf <- female%>%
  filter(sw201a == "1 Yes" | (Gender == "2 Female" & sw201b == "1 Yes")  |sw201c == "1 Yes" |sw201d == "1 Yes") %>%
  summarise(freq_yes2mf = sum(stateindividualweight))

# Calculate the frequency of "2 No" in all of the specified columns
no_frequency2mf <- female%>%
  filter(sw201a == "2 No" & (Gender == "2 Female" & sw201b == "2 No")  & sw201c == "2 No" & sw201d == "2 No" ) %>%
  summarise(freq_no2mf = sum(stateindividualweight))

# Combine the frequencies and calculate the proportions
total_responses2mf <- sum(female$stateindividualweight)
yes_proportion2mf <- (yes_frequency2mf$freq_yes2mf / total_responses2mf)*100
no_proportion2mf <- (no_frequency2mf$freq_no2mf / total_responses2mf)*100

# Create a data frame with the results
results2mf <- data.frame(
  Response = c("1 Yes", "2 No", "NA"),
  Weighted_Proportion = c(yes_proportion2mf, no_proportion2mf, 100 - (yes_proportion2mf + no_proportion2mf))
)

# Print the results
print(results2mf)
```




**II. BENEFICIARIES**

*(i) Male*

*1. Beneficiaries - Yes*
```{r}
benefit_yesm<- awarem%>%
  filter(sw202a == "1 Yes" | sw202c == "1 Yes" |sw202d == "1 Yes" | sw202e == "1 Yes" )
```

*2. Beneficiaries - No*
```{r}
benefit_nom<- awarem%>%
  filter(sw202a == "2 No" & sw202c == "2 No" & sw202d == "2 No" & sw202e == "2 No")
```


```{r}
# Calculate the frequency of "1 Yes" in any of the specified columns
yes_freq3 <- awarem%>%
  filter(sw202a == "1 Yes" |sw202c == "1 Yes" |sw202d == "1 Yes" | sw202e == "1 Yes") %>%
  summarise(freq_yes3 = n())

# Calculate the frequency of "2 No" in all of the specified columns
no_freq3 <- awarem%>%
  filter(sw202a == "2 No" & sw202c == "2 No" & sw202d == "2 No" & sw202e == "2 No") %>%
  summarise(freq_no3 = n())

# Print the results
cat("Frequency '1 Yes':", yes_freq3$freq_yes3, "\n")
cat("Frequency '2 No':", no_freq3$freq_no3, "\n")

# Calculate the frequency of "1 Yes" in any of the specified columns
yes_frequency3 <- awarem%>%
  filter(sw202a == "1 Yes" | sw202c == "1 Yes" |sw202d == "1 Yes" | sw202e == "1 Yes") %>%
  summarise(freq_yes3 = sum(stateindividualweight))

# Calculate the frequency of "2 No" in all of the specified columns
no_frequency3 <- awarem%>%
  filter(sw202a == "2 No" & sw202c == "2 No" & sw202d == "2 No" & sw202e == "2 No") %>%
  summarise(freq_no3 = sum(stateindividualweight))

# Combine the frequencies and calculate the proportions
total_responses3 <- sum(awarem$stateindividualweight)
yes_proportion3 <- (yes_frequency3$freq_yes3 / total_responses3)*100
no_proportion3 <- (no_frequency3$freq_no3 / total_responses3)*100

# Create a data frame with the results
results3 <- data.frame(
  Response = c("1 Yes", "2 No", "NA"),
  Weighted_Proportion = c(yes_proportion3, no_proportion3, 100 - (yes_proportion3 + no_proportion3))
)

# Print the results
print(results3)

```



*(ii) Female*

*1. Beneficiaries - Yes*
```{r}
benefit_yesmf<- awaremf%>%
  filter(sw202a == "1 Yes" | (Gender == "2 Female" & sw201b == "1 Yes")  |sw202c == "1 Yes" |sw202d == "1 Yes" | sw202e == "1 Yes" )
```

*2. Beneficiaries - No*
```{r}
benefit_nomf<- awaremf%>%
  filter(sw202a == "2 No" & (Gender == "2 Female" & sw201b == "1 Yes")  & sw202c == "2 No" & sw202d == "2 No" & sw202e == "2 No")
```


```{r}
# Calculate the frequency of "1 Yes" in any of the specified columns
yes_freq3a <- awaremf%>%
  filter(sw202a == "1 Yes" |(Gender == "2 Female" & sw201b == "1 Yes")  | sw202c == "1 Yes" |sw202d == "1 Yes" | sw202e == "1 Yes") %>%
  summarise(freq_yes3a = n())

# Calculate the frequency of "2 No" in all of the specified columns
no_freq3a <- awaremf%>%
  filter(sw202a == "2 No" & sw202c == "2 No" & (Gender == "2 Female" & sw201b == "1 Yes") & sw202d == "2 No" & sw202e == "2 No") %>%
  summarise(freq_no3a = n())

# Print the results
cat("Frequency '1 Yes':", yes_freq3a$freq_yes3a, "\n")
cat("Frequency '2 No':", no_freq3a$freq_no3a, "\n")

# Calculate the frequency of "1 Yes" in any of the specified columns
yes_frequency3a <- awaremf%>%
  filter(sw202a == "1 Yes" | sw202c == "1 Yes" |(Gender == "2 Female" & sw201b == "1 Yes")  | sw202d == "1 Yes" | sw202e == "1 Yes") %>%
  summarise(freq_yes3a = sum(stateindividualweight))

# Calculate the frequency of "2 No" in all of the specified columns
no_frequency3a <- awaremf%>%
  filter(sw202a == "2 No" & sw202c == "2 No" & (Gender == "2 Female" & sw201b == "1 Yes")  & sw202d == "2 No" & sw202e == "2 No") %>%
  summarise(freq_no3a = sum(stateindividualweight))

# Combine the frequencies and calculate the proportions
total_responses3a <- sum(awaremf$stateindividualweight)
yes_proportion3a <- (yes_frequency3a$freq_yes3a / total_responses3a)*100
no_proportion3a <- (no_frequency3a$freq_no3a / total_responses3a)*100

# Create a data frame with the results
results3a <- data.frame(
  Response = c("1 Yes", "2 No", "NA"),
  Weighted_Proportion = c(yes_proportion3a, no_proportion3a, 100 - (yes_proportion3a + no_proportion3a))
)

# Print the results
print(results3a)

```



**III. CONCESSIONS**

*(i) Male*
```{r}
# Create the frequency distribution table
frequency1m <- table(male$sw211)
print(frequency1m)

# Define the survey design
design1m <- svydesign(id = ~1, weights = ~stateindividualweight, data = male)

# Create a weighted frequency distribution table
svytable_design1m <- svytable(~sw211, design = design1m)
print(svytable_design1m)

# Proportion table from the weighted frequency distribution
weighted_proportion_table1m <- prop.table(svytable_design1m) * 100  
print(round(weighted_proportion_table1m, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df1m <- as.data.frame(weighted_proportion_table1m)
```


*(ii) Female*
```{r}
# Create the frequency distribution table
frequency1mf <- table(female$sw211)
print(frequency1mf)

# Define the survey design
design1mf <- svydesign(id = ~1, weights = ~stateindividualweight, data = female)

# Create a weighted frequency distribution table
svytable_design1mf <- svytable(~sw211, design = design1mf)
print(svytable_design1mf)

# Proportion table from the weighted frequency distribution
weighted_proportion_table1mf <- prop.table(svytable_design1mf) * 100  
print(round(weighted_proportion_table1mf, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df1mf <- as.data.frame(weighted_proportion_table1mf)
```


**1. Aware/heard about the “Maintenance and Welfare of Parents and Senior Citizens Act”**

*(i) Male*
```{r}
# Create the frequency distribution table
frequency2m <- table(male$sw213)
print(frequency2m)

# Define the survey design
design2m <- svydesign(id = ~1, weights = ~stateindividualweight, data = male)

# Create a weighted frequency distribution table
svytable_design2m <- svytable(~sw213, design = design2m)
print(svytable_design2m)

# Proportion table from the weighted frequency distribution
weighted_proportion_table2m <- prop.table(svytable_design2m) * 100  
print(round(weighted_proportion_table2m, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df2m <- as.data.frame(weighted_proportion_table2m)
```


*(ii) Female*
```{r}
# Create the frequency distribution table
frequency2mf <- table(female$sw213)
print(frequency2mf)

# Define the survey design
design2mf <- svydesign(id = ~1, weights = ~stateindividualweight, data = female)

# Create a weighted frequency distribution table
svytable_design2mf <- svytable(~sw213, design = design2mf)
print(svytable_design2mf)

# Proportion table from the weighted frequency distribution
weighted_proportion_table2mf <- prop.table(svytable_design2mf) * 100  
print(round(weighted_proportion_table2mf, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df2mf <- as.data.frame(weighted_proportion_table2mf)
```