---
title: "Social Relationship"
author: "Mizza"
date: "2024-06-14"
output: html_document
---

```{r}
#| label: setup
#| warning: false
#| echo: false

library(ggplot2)
library(readxl)
library(dplyr)
library(tidyverse)
library(tidyr)
library(survey)
library(ggsankey)

Household <- read_excel("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/2_LASI_W1_Household_v4 1.xlsx")
Individual <- read_excel("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/3_LASI_W1_Individual_data 1.xlsx")
merged_data <- merge (Individual, Household, by = "hhid", all = TRUE)
roster <- read_excel ("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/1_LASI_W1_HH_roster 1.xlsx")
final_data <- merge (merged_data, roster, by = "hhid", all = TRUE)
```


**DATA OF VULNERABLE GROUP - SENIOR CITIZENS**

```{r}
final_data <- final_data%>%
  rename(Age = dm005)
```

```{r}

##TO APPLY AGE FILTER##
create_age_category <- function(Age) {
  if (is.na(Age)) {
    return(NA)
  }
  
  if (Age >= 60 & Age <= 69) {
    return("Young Old")
  } else if (Age >= 70 & Age <= 79) {
    return("Old")
  } else if (Age >= 80) {
    return("Very Old")
  } else {
    return(NA) 
  }
}
final_data$AgeCategory <- sapply(final_data$Age, create_age_category)

final_data <- final_data[final_data$AgeCategory %in% c("Young Old", "Old", "Very Old"), ]
```


**EDUCATION BUCKET**

```{r}
final_data <- final_data %>%
  mutate(Education_level = case_when(
    dm006 == "2 No" ~ "Uneducated",
    dm008 %in% c("1 Less than Primary (Standard 1-4)", 
                 "2 Primary Completed (Standard 5-7)", 
                 "3 Middle Completed (Standard 8- 9)") ~ "Primary School",
    dm008 == "4 Secondary School/Matriculation completed" ~ "Secondary School",
    dm008 %in% c("5 Higher Secondary/Intermediate/Senior Secondary completed", 
                 "6 Diploma and certificate holders") ~ "Senior Secondary School",
    dm008 %in% c("7 Graduate degree (B.A., B.Sc., B. Com.) completed", 
                 "8 Post-graduate degree or (M.A., M.Sc., M. Com.) above (M.Phil, Ph.D., Post-Doc) completed", 
                 "9 Professional course/degree (B.Ed, BE, B.Tech, MBBS, BHMS, BAMS, B.Pharm, BCS, BCA, BBA, LLB, BVSc., B. Arch, M.Ed, ME, M.Tech, MD, M.Pharm, MCS, MCA, MBA,LLM, MVSc., M. Arch, MS, CA, CS, CWA)Completed") ~ "Tertiary Education",
    TRUE ~ "Other"
  ))
```



**I. Interaction with friends and family**

**1. Close Relationship**

```{r}
final_data <- final_data %>%
  rename(family = fs323)
```

**1. Family Relation - Yes**
```{r}
fam_relation_yes<- final_data%>%
  filter(fs323s1 == "1 Yes"| fs323s2 == "1 Yes"|fs323s3 == "1 Yes"|fs323s4 == "1 Yes"|fs323s5 == "1 Yes"|fs323s6 == "1 Yes"|fs323s7 == "1 Yes"|fs323s8 == "1 Yes"|fs323s9 == "1 Yes"|fs323s10 == "1 Yes"|fs323s11 == "1 Yes"|fs323s12 == "1 Yes"|fs323s13 == "1 Yes" )
```

**2. Friends Relation - Yes**
```{r}
frnds_relation_yes<- final_data%>%
  filter(fs323s14 == "1 Yes")
```

**3. Relation with nobody**
```{r}
relation_no<- final_data%>%
  filter(fs323s16 == "1 Yes")
```


*Close relation with anybody*
```{r}
# Calculate the frequency of "1 Yes" in any of the specified columns
yes_freq1 <- final_data%>%
  filter(fs323s1 == "1 Yes"| fs323s2 == "1 Yes"|fs323s3 == "1 Yes"|fs323s4 == "1 Yes"|fs323s5 == "1 Yes"|fs323s6 == "1 Yes"|fs323s7 == "1 Yes"|fs323s8 == "1 Yes"|fs323s9 == "1 Yes"|fs323s10 == "1 Yes"|fs323s11 == "1 Yes"|fs323s12 == "1 Yes"|fs323s13 == "1 Yes"|fs323s14 == "1 Yes"|fs323s15 == "1 Yes") %>%
  summarise(freq_yes1 = n())

# Calculate the frequency of "2 No" in all of the specified columns
no_freq1 <- final_data%>%
  filter(fs323s16 == "1 Yes" ) %>%
  summarise(freq_no1 = n())

# Print the results
cat("Frequency '1 Yes':", yes_freq1$freq_yes1, "\n")
cat("Frequency '2 No':", no_freq1$freq_no1, "\n")

# Calculate the frequency of "1 Yes" in any of the specified columns
yes_frequency1 <- final_data%>%
  filter(fs323s1 == "1 Yes"| fs323s2 == "1 Yes"|fs323s3 == "1 Yes"|fs323s4 == "1 Yes"|fs323s5 == "1 Yes"|fs323s6 == "1 Yes"|fs323s7 == "1 Yes"|fs323s8 == "1 Yes"|fs323s9 == "1 Yes"|fs323s10 == "1 Yes"|fs323s11 == "1 Yes"|fs323s12 == "1 Yes"|fs323s13 == "1 Yes"|fs323s14 == "1 Yes"|fs323s15 == "1 Yes") %>%
  summarise(freq_yes1 = sum(stateindividualweight))

# Calculate the frequency of "2 No" in all of the specified columns
no_frequency1 <- final_data%>%
  filter(fs323s16 == "1 Yes") %>%
  summarise(freq_no1 = sum(stateindividualweight))

# Combine the frequencies and calculate the proportions
total_responses1 <- sum(final_data$stateindividualweight)
yes_proportion1 <- (yes_frequency1$freq_yes1 / total_responses1)*100
no_proportion1 <- (no_frequency1$freq_no1 / total_responses1)*100

# Create a data frame with the results
results1 <- data.frame(
  Response = c("1 Yes", "0 No", "NA"),
  Weighted_Proportion = c(yes_proportion1, no_proportion1, 100 - (yes_proportion1 + no_proportion1))
)

# Print the results
print(results1)


```




**2. Friends**

```{r}
final_data <- final_data %>%
  rename(friends = fs324)
```


```{r}
count_friends <- sum(!is.na(final_data$friends))

# Print the result
print(count_friends)

# Create the frequency distribution table
frequency1 <- table(final_data$friends)
print(frequency1)

# Proportion table
proportion_table1 <- prop.table(frequency1) * 100  
print(round(proportion_table1, digits=2))

# Define the survey design
design1 <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design1 <- svytable(~friends, design = design1)
print(svytable_design1)

# Proportion table from the weighted frequency distribution
weighted_proportion_table1 <- prop.table(svytable_design1) * 100  
print(round(weighted_proportion_table1, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df1 <- as.data.frame(weighted_proportion_table1)
```



**2. 1. FRIENDS - YES**

```{r}
friends<- final_data%>%
  filter(friends == "1 Yes")
```


*a. Meet up*

```{r}
count_fs326 <- sum(!is.na(friends$fs326))

# Print the result
print(count_fs326)

# Create the frequency distribution table
frequency2 <- table(friends$fs326)
print(frequency2)

# Define the survey design
design2 <- svydesign(id = ~1, weights = ~stateindividualweight, data = friends)

# Create a weighted frequency distribution table
svytable_design2 <- svytable(~fs326, design = design2)
print(svytable_design2)

# Proportion table from the weighted frequency distribution
weighted_proportion_table2 <- prop.table(svytable_design2) * 100  
print(round(weighted_proportion_table2, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df2 <- as.data.frame(weighted_proportion_table2)
```


*b. e-mail/call*

```{r}
count_fs327 <- sum(!is.na(friends$fs327))

# Print the result
print(count_fs327)

# Create the frequency distribution table
frequency3 <- table(friends$fs327)
print(frequency3)

# Define the survey design
design3 <- svydesign(id = ~1, weights = ~stateindividualweight, data = friends)

# Create a weighted frequency distribution table
svytable_design3 <- svytable(~fs327, design = design3)
print(svytable_design3)

# Proportion table from the weighted frequency distribution
weighted_proportion_table3 <- prop.table(svytable_design3) * 100  
print(round(weighted_proportion_table3, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df3 <- as.data.frame(weighted_proportion_table3)
```





**II. Social Activities**


**1. Member of any Social Group**

```{r}
final_data<- final_data%>%
  rename(social_grp = fs501)
```

```{r}
count_social_grp <- sum(!is.na(final_data$social_grp))

# Print the result
print(count_social_grp)

# Create the frequency distribution table
frequency4 <- table(final_data$social_grp)
print(frequency4)

# Define the survey design
design4 <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4 <- svytable(~social_grp, design = design4)
print(svytable_design4)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4 <- prop.table(svytable_design4) * 100  
print(round(weighted_proportion_table4, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4 <- as.data.frame(weighted_proportion_table4)
```



**2. Involvement in any Social Activities **

*1. Eat out of the house*
```{r}
final_data<- final_data%>%
  rename(Eat_out_of_the_house = fs504)
```

```{r}
count_Eat_out_of_the_house <- sum(!is.na(final_data$Eat_out_of_the_house))

# Print the result
print(count_Eat_out_of_the_house)

# Create the frequency distribution table
frequency4a <- table(final_data$Eat_out_of_the_house)
print(frequency4a)

# Define the survey design
design4a <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4a <- svytable(~Eat_out_of_the_house, design = design4a)
print(svytable_design4a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4a <- prop.table(svytable_design4a) * 100  
print(round(weighted_proportion_table4a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4a <- as.data.frame(weighted_proportion_table4a)
```


*2. Go to park/beach for relaxing/entertainment *
```{r}
final_data<- final_data%>%
  rename(Go_to_park_beach_for_relaxing_entertainment = fs505)
```

```{r}
# Create the frequency distribution table
frequency4b <- table(final_data$Go_to_park_beach_for_relaxing_entertainment)
print(frequency4b)

# Define the survey design
design4b <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4b <- svytable(~Go_to_park_beach_for_relaxing_entertainment, design = design4b)
print(svytable_design4b)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4b <- prop.table(svytable_design4b) * 100  
print(round(weighted_proportion_table4b, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4b <- as.data.frame(weighted_proportion_table4b)
```


*3.  Play cards or indoor games*
```{r}
final_data<- final_data%>%
  rename(Play_cards_or_indoor_games = fs506)
```

```{r}
# Create the frequency distribution table
frequency4c <- table(final_data$Play_cards_or_indoor_games)
print(frequency4c)

# Define the survey design
design4c <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4c <- svytable(~Play_cards_or_indoor_games, design = design4c)
print(svytable_design4c)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4c <- prop.table(svytable_design4c) * 100  
print(round(weighted_proportion_table4c, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4c <- as.data.frame(weighted_proportion_table4c)
```


*4.  Play out door games/sports/exercise/jog/yoga*
```{r}
final_data<- final_data%>%
  rename(Play_out_door = fs507)
```

```{r}
# Create the frequency distribution table
frequency4d <- table(final_data$Play_out_door)
print(frequency4d)

# Define the survey design
design4d <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4d <- svytable(~Play_out_door, design = design4d)
print(svytable_design4d)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4d <- prop.table(svytable_design4d) * 100  
print(round(weighted_proportion_table4d, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4d <- as.data.frame(weighted_proportion_table4d)
```


*5. Visit relatives /friends*
```{r}
final_data<- final_data%>%
  rename(Visit_relatives_friends = fs508)
```

```{r}
# Create the frequency distribution table
frequency4e <- table(final_data$Visit_relatives_friends)
print(frequency4e)

# Define the survey design
design4e <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4e <- svytable(~Visit_relatives_friends, design = design4e)
print(svytable_design4e)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4e <- prop.table(svytable_design4e) * 100  
print(round(weighted_proportion_table4e, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4e <- as.data.frame(weighted_proportion_table4e)
```


*6. Attend cultural performances /shows/Cinema*
```{r}
final_data<- final_data%>%
  rename(Attend_cultural_performances= fs509)
```

```{r}
# Create the frequency distribution table
frequency4f <- table(final_data$Attend_cultural_performances)
print(frequency4f)

# Define the survey design
design4f <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4f <- svytable(~Attend_cultural_performances, design = design4f)
print(svytable_design4f)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4f <- prop.table(svytable_design4f) * 100  
print(round(weighted_proportion_table4f, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4f <- as.data.frame(weighted_proportion_table4f)
```


*7.  Attend religious functions /events such as bhajan/satsang/prayer*
```{r}
final_data<- final_data%>%
  rename(Attend_religious_functions = fs510)
```

```{r}
# Create the frequency distribution table
frequency4g <- table(final_data$Attend_religious_functions)
print(frequency4g)

# Define the survey design
design4g <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4g <- svytable(~Attend_religious_functions, design = design4g)
print(svytable_design4g)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4g <- prop.table(svytable_design4g) * 100  
print(round(weighted_proportion_table4g, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4g <- as.data.frame(weighted_proportion_table4g)
```


*8. Attend political/community/organization group meetings*
```{r}
final_data<- final_data%>%
  rename(Attend_group_meetings = fs511)
```

```{r}
# Create the frequency distribution table
frequency4h <- table(final_data$Attend_group_meetings)
print(frequency4h)

# Define the survey design
design4h <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4h <- svytable(~Attend_group_meetings, design = design4h)
print(svytable_design4h)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4h <- prop.table(svytable_design4h) * 100  
print(round(weighted_proportion_table4h, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4h <- as.data.frame(weighted_proportion_table4h)
```


*9. .Read books/newspapers/magazines*
```{r}
# Create the frequency distribution table
frequency4i <- table(final_data$fs512)
print(frequency4i)

# Define the survey design
design4i <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4i <- svytable(~fs512, design = design4i)
print(svytable_design4i)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4i <- prop.table(svytable_design4i) * 100  
print(round(weighted_proportion_table4i, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4i <- as.data.frame(weighted_proportion_table4i)
```


*10. Watch television/listen radio*
```{r}
# Create the frequency distribution table
frequency4j <- table(final_data$fs513)
print(frequency4j)

# Define the survey design
design4j <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4j <- svytable(~fs513, design = design4j)
print(svytable_design4j)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4j <- prop.table(svytable_design4j) * 100  
print(round(weighted_proportion_table4j, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4j <- as.data.frame(weighted_proportion_table4j)
```


*11.Use a computer for e-mail/net surfing etc.*
```{r}
# Create the frequency distribution table
frequency4k <- table(final_data$fs514)
print(frequency4k)

# Define the survey design
design4k <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design4k <- svytable(~fs514, design = design4k)
print(svytable_design4k)

# Proportion table from the weighted frequency distribution
weighted_proportion_table4k <- prop.table(svytable_design4k) * 100  
print(round(weighted_proportion_table4k, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df4k <- as.data.frame(weighted_proportion_table4k)
```

```{r}
# Using dplyr to create the new column with the total score
final_data <- final_data %>%
  mutate(Social_activity_INDEX = rowSums(across(c("Eat_out_of_the_house","Go_to_park_beach_for_relaxing_entertainment","Play_cards_or_indoor_games","Play_out_door", "Visit_relatives_friends", "Attend_cultural_performances", "Attend_religious_functions", "Attend_group_meetings"),
                                                        ~ ifelse(. == "7 Never/Not relevant		
", 0,
                                                                 ifelse(. == "1 Daily		
", 7,
                                                                        ifelse(. == "2 Several times a week", 6,
                                                                               ifelse(. == "3 Once a week", 5,
                                                                                      ifelse(. == "4 Several times a month", 4,
                                                                                             ifelse(. == "5 At least once a month", 3,
                                                                                                    ifelse(. == "6 Rarely/Once in a year", 2,
                                                                                             ifelse(. == "5 Less than once a year", 1, NA)))))))))))                                                                         
                                                      

# Define the survey design
design <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Corrected variable name usage
Social_activity_INDEX_vars <- c("Social_activity_INDEX") # This should match the column name created in mutate

# Initialize an empty list to store the proportion tables
proportion_tables <- list()

# Generate and store the proportion table for each variable
for (var_name in Social_activity_INDEX_vars) {
  # Construct the formula directly using the variable name
  var_formula <- as.formula(paste0("~", var_name))
  
  # Use the formula in svytable to get the frequency table
  freq_table <- svytable(var_formula, design = design)
  
  # Convert the frequency table to proportions and store it in the list
  proportion_tables[[paste0(var_name, "_proportions")]] <- freq_table / sum(freq_table)
}

# Combine the proportion tables into a single table
combined_proportion_table_Social_activity_INDEX <- do.call(rbind, lapply(proportion_tables, function(table) {
  # Add a column for the variable name
  table$Variable <- rep(names(proportion_tables), each = nrow(table) / length(proportion_tables))
  return(table)
}))

# Print the combined proportion table
print(combined_proportion_table_Social_activity_INDEX)
                                                  
# Convert weighted_proportion_table to a data frame
weighted_proportion_df <- as.data.frame(combined_proportion_table_Social_activity_INDEX)                                      
```

**III. LONELINESS**

```{r}
loneliness<- final_data%>%
  filter(fs323s16 == "1 Yes" & friends == "2 No" & fs326 == "5 Never" & fs327 == "5 Never" & social_grp == "2 No" & Eat_out_of_the_house == "7 Never/Not relevant" & Go_to_park_beach_for_relaxing_entertainment == "7 Never/Not relevant" & Play_cards_or_indoor_games == "7 Never/Not relevant"& Play_out_door == "7 Never/Not relevant"& Visit_relatives_friends == "7 Never/Not relevant" & Attend_cultural_performances == "7 Never/Not relevant" & Attend_religious_functions== "7 Never/Not relevant"& Attend_group_meetings == "7 Never/Not relevant")
```
