---
title: "Employment Situation of Senior Citizens - Gender wise"
author: "Mizza"
date: "2024-06-24"
output: html_document
---

```{r}
#| label: setup
#| warning: false
#| echo: false

library(ggplot2)
library(readxl)
library(dplyr)
library(tidyverse)
library(tidyr)
library(survey)
library(ggsankey)

Household <- read_excel("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/2_LASI_W1_Household_v4 1.xlsx")
Individual <- read_excel("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/3_LASI_W1_Individual_data 1.xlsx")
merged_data <- merge (Individual, Household, by = "hhid", all = TRUE)
roster <- read_excel ("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/1_LASI_W1_HH_roster 1.xlsx")
final_data <- merge (merged_data, roster, by = "hhid", all = TRUE)
```


**DATA OF VULNERABLE GROUP - SENIOR CITIZENS**

```{r}
final_data <- final_data%>%
  rename(Age = dm005)
```

```{r}

##TO APPLY AGE FILTER##
create_age_category <- function(Age) {
  if (is.na(Age)) {
    return(NA)
  }
  
  if (Age >= 60 & Age <= 69) {
    return("Young Old")
  } else if (Age >= 70 & Age <= 79) {
    return("Old")
  } else if (Age >= 80) {
    return("Very Old")
  } else {
    return(NA) 
  }
}
final_data$AgeCategory <- sapply(final_data$Age, create_age_category)

final_data <- final_data[final_data$AgeCategory %in% c("Young Old", "Old", "Very Old"), ]
```

**EDUCATION BUCKET**

```{r}
final_data <- final_data %>%
  mutate(Education_level = case_when(
    dm006 == "2 No" ~ "Uneducated",
    dm008 %in% c("1 Less than Primary (Standard 1-4)", 
                 "2 Primary Completed (Standard 5-7)", 
                 "3 Middle Completed (Standard 8- 9)") ~ "Primary School",
    dm008 == "4 Secondary School/Matriculation completed" ~ "Secondary School",
    dm008 %in% c("5 Higher Secondary/Intermediate/Senior Secondary completed", 
                 "6 Diploma and certificate holders") ~ "Senior Secondary School",
    dm008 %in% c("7 Graduate degree (B.A., B.Sc., B. Com.) completed", 
                 "8 Post-graduate degree or (M.A., M.Sc., M. Com.) above (M.Phil, Ph.D., Post-Doc) completed", 
                 "9 Professional course/degree (B.Ed, BE, B.Tech, MBBS, BHMS, BAMS, B.Pharm, BCS, BCA, BBA, LLB, BVSc., B. Arch, M.Ed, ME, M.Tech, MD, M.Pharm, MCS, MCA, MBA,LLM, MVSc., M. Arch, MS, CA, CS, CWA)Completed") ~ "Tertiary Education",
    TRUE ~ "Other"
  ))
```

```{r}
final_data <- final_data %>%
  rename(Gender = dm003)
```



**CURRENT EMPLOYMENT SCENARIO**

```{r}
final_data<-final_data%>%
  rename(Employed = we004)
```

```{r}

# Replace NA values in the Employed column with "Never worked"
final_data$Employed[is.na(final_data$Employed)] <- "Never worked"


# Create the frequency distribution table
frequency5 <- table(final_data$Employed)
print(frequency5)
 
# Define the survey design
design5 <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design5 <- svytable(~Employed, design = design5)
print(svytable_design5)

# Proportion table from the weighted frequency distribution
weighted_proportion_table5 <- prop.table(svytable_design5) * 100  
print(round(weighted_proportion_table5, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df5 <- as.data.frame(weighted_proportion_table5)
```


*A.Gender Analysis*
```{r}
final_data<- final_data%>%
  rename(Employed_3_months = we001)
```


*(i) Male*

```{r}
male<- final_data%>%
  filter(Gender == "1 Male")
```

```{r}
# Create the frequency distribution table
frequency1 <- table(male$Employed)
print(frequency1)

# Define the survey design
design1 <- svydesign(id = ~1, weights = ~stateindividualweight, data = male)

# Create a weighted frequency distribution table
svytable_design1 <- svytable(~Employed, design = design1)
print(svytable_design1)

# Proportion table from the weighted frequency distribution
weighted_proportion_table1 <- prop.table(svytable_design1) * 100  
print(round(weighted_proportion_table1, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df1 <- as.data.frame(weighted_proportion_table1)

```



*(ii) Female*

```{r}
female<- final_data%>%
  filter(Gender == "2 Female")
```

```{r}
# Create the frequency distribution table
frequency14 <- table(female$Employed)
print(frequency14)

# Define the survey design
design14 <- svydesign(id = ~1, weights = ~stateindividualweight, data = female)

# Create a weighted frequency distribution table
svytable_design14 <- svytable(~Employed, design = design14)
print(svytable_design14)

# Proportion table from the weighted frequency distribution
weighted_proportion_table14 <- prop.table(svytable_design14) * 100  
print(round(weighted_proportion_table14, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df14 <- as.data.frame(weighted_proportion_table14)

```



**II.1. CURRENTLY NOT WORKING - Reason**

*(i) Male*

```{r}
currently_not_working_male<- male%>%
  filter(Employed == "2 No")
```

```{r}
currently_not_working_male <- currently_not_working_male %>%
  rename(Reason_current_not_working = we005)
```

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search2 <- sum(is.na(currently_not_working_male$Reason_current_not_working))

# Print the result
print(num_NA_job_search2)
```

```{r}
# Create the frequency distribution table
frequency5 <- table(currently_not_working_male$Reason_current_not_working)
print(frequency5)

# Proportion table
proportion_table5 <- prop.table(frequency5) * 100 
print(round(proportion_table5, digits=2))

# Define the survey design
design5 <- svydesign(id = ~1, weights = ~stateindividualweight, data = currently_not_working_male)

# Create a weighted frequency distribution table
svytable_design5 <- svytable(~Reason_current_not_working, design = design5)
print(svytable_design5)

# Proportion table from the weighted frequency distribution
weighted_proportion_table5 <- prop.table(svytable_design5) * 100  
print(round(weighted_proportion_table5, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df5 <- as.data.frame(weighted_proportion_table5)

```



*(ii) Female*

```{r}
currently_not_working_female<- female%>%
  filter(Employed == "2 No")
```

```{r}
currently_not_working_female <- currently_not_working_female %>%
  rename(Reason_current_not_working = we005)
```

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search2 <- sum(is.na(currently_not_working_female$Reason_current_not_working))

# Print the result
print(num_NA_job_search2)
```

```{r}
# Create the frequency distribution table
frequency5a <- table(currently_not_working_female$Reason_current_not_working)
print(frequency5a)

# Define the survey design
design5a <- svydesign(id = ~1, weights = ~stateindividualweight, data = currently_not_working_female)

# Create a weighted frequency distribution table
svytable_design5a <- svytable(~Reason_current_not_working, design = design5a)
print(svytable_design5a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table5a <- prop.table(svytable_design5a) * 100  
print(round(weighted_proportion_table5a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df5a <- as.data.frame(weighted_proportion_table5a)
```


**III.1. CURRENTLY WORKING - Occupation**

*(i) Male*

```{r}
labour_force_male<- male%>%
  filter(Employed == "1 Yes")
```

```{r}
labour_force_male <- labour_force_male %>%
  rename(Occupation = we027)
```

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search2 <- sum(is.na(labour_force_male$Occupation))

# Print the result
print(num_NA_job_search2)
```

```{r}
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "9", "9 Elementary occupations", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "4", "4 Clerks", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "5", "5 Service workers and shop and market sales workers", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "6", "6 Skilled agricultural and fishery workers", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "7", "7 Craft and related trade workers", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "8", "8 Plant and machine operators and assemblers", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "10", "10 Workers not classified anywhere", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "11", "11 Other", labour_force_male$Occupation)
```

```{r}
# Create the frequency distribution table
frequency6 <- table(labour_force_male$Occupation)
print(frequency6)

# Define the survey design
design6 <- svydesign(id = ~1, weights = ~stateindividualweight, data = labour_force_male)

# Create a weighted frequency distribution table
svytable_design6 <- svytable(~Occupation, design = design6)
print(svytable_design6)

# Proportion table from the weighted frequency distribution
weighted_proportion_table6 <- prop.table(svytable_design6) * 100  
print(round(weighted_proportion_table6, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df6 <- as.data.frame(weighted_proportion_table6)
```



*(ii) Female*

```{r}
currently_not_working_female<- female%>%
  filter(Employed == "2 No")
```

```{r}
currently_not_working_female <- currently_not_working_female %>%
  rename(Reason_current_not_working = we005)
```

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search2 <- sum(is.na(currently_not_working_female$Reason_current_not_working))

# Print the result
print(num_NA_job_search2)
```

```{r}
# Create the frequency distribution table
frequency5a <- table(currently_not_working_female$Reason_current_not_working)
print(frequency5a)

# Define the survey design
design5a <- svydesign(id = ~1, weights = ~stateindividualweight, data = currently_not_working_female)

# Create a weighted frequency distribution table
svytable_design5a <- svytable(~Reason_current_not_working, design = design5a)
print(svytable_design5a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table5a <- prop.table(svytable_design5a) * 100  
print(round(weighted_proportion_table5a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df5a <- as.data.frame(weighted_proportion_table5a)
```



*(i) Male*

```{r}
labour_force_male<- male%>%
  filter(Employed == "1 Yes")
```

```{r}
labour_force_male <- labour_force_male %>%
  rename(Occupation = we027)
```

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search2 <- sum(is.na(labour_force_male$Occupation))

# Print the result
print(num_NA_job_search2)
```

```{r}
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "9", "9 Elementary occupations", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "4", "4 Clerks", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "5", "5 Service workers and shop and market sales workers", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "6", "6 Skilled agricultural and fishery workers", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "7", "7 Craft and related trade workers", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "8", "8 Plant and machine operators and assemblers", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "10", "10 Workers not classified anywhere", labour_force_male$Occupation)
labour_force_male$Occupation <- ifelse(labour_force_male$Occupation == "11", "11 Other", labour_force_male$Occupation)
```

```{r}
# Create the frequency distribution table
frequency6 <- table(labour_force_male$Occupation)
print(frequency6)

# Define the survey design
design6 <- svydesign(id = ~1, weights = ~stateindividualweight, data = labour_force_male)

# Create a weighted frequency distribution table
svytable_design6 <- svytable(~Occupation, design = design6)
print(svytable_design6)

# Proportion table from the weighted frequency distribution
weighted_proportion_table6 <- prop.table(svytable_design6) * 100  
print(round(weighted_proportion_table6, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df6 <- as.data.frame(weighted_proportion_table6)
```



*(ii) Female*

```{r}
labour_force_female<- female%>%
  filter(Employed == "1 Yes")
```

```{r}
labour_force_female <- labour_force_female %>%
  rename(Occupation = we027)
```

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search2 <- sum(is.na(labour_force_female$Occupation))

# Print the result
print(num_NA_job_search2)
```

```{r}
labour_force_female$Occupation <- ifelse(labour_force_female$Occupation == "9", "9 Elementary occupations", labour_force_female$Occupation)
labour_force_female$Occupation <- ifelse(labour_force_female$Occupation == "4", "4 Clerks", labour_force_female$Occupation)
labour_force_female$Occupation <- ifelse(labour_force_female$Occupation == "5", "5 Service workers and shop and market sales workers", labour_force_female$Occupation)
labour_force_female$Occupation <- ifelse(labour_force_female$Occupation == "6", "6 Skilled agricultural and fishery workers", labour_force_female$Occupation)
labour_force_female$Occupation <- ifelse(labour_force_female$Occupation == "7", "7 Craft and related trade workers", labour_force_female$Occupation)
labour_force_female$Occupation <- ifelse(labour_force_female$Occupation == "8", "8 Plant and machine operators and assemblers", labour_force_female$Occupation)
labour_force_female$Occupation <- ifelse(labour_force_female$Occupation == "10", "10 Workers not classified anywhere", labour_force_female$Occupation)
labour_force_female$Occupation <- ifelse(labour_force_female$Occupation == "11", "11 Other", labour_force_female$Occupation)
```

```{r}
# Create the frequency distribution table
frequency6a <- table(labour_force_female$Occupation)
print(frequency6a)

# Define the survey design
design6a <- svydesign(id = ~1, weights = ~stateindividualweight, data = labour_force_female)

# Create a weighted frequency distribution table
svytable_design6a <- svytable(~Occupation, design = design6a)
print(svytable_design6a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table6a <- prop.table(svytable_design6a) * 100  
print(round(weighted_proportion_table6a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df6a <- as.data.frame(weighted_proportion_table6a)
```



**B. FINANCIAL SECURITY**


*Combining currently working and not working*
```{r}
current_scenario_male<- bind_rows(labour_force_male, currently_not_working_male)
```

```{r}
current_scenario_female<- bind_rows(labour_force_female, currently_not_working_female)
```


**I. Financial Security - Pension**


*(i) Male*

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search3 <- sum(is.na(current_scenario_male$we412))

# Print the result
print(num_NA_job_search3)
```


```{r}

current_scenario_male <- current_scenario_male %>%
  mutate(we412 = ifelse(is.na(we412), "NA", we412),
         we412 = ifelse(we412 %in% c("1 Currently receiving", "2 Expected to receive in future"), 
                        "Currently receiving or expected to receive", we412))


# Create the frequency distribution table
frequency8 <- table(current_scenario_male$we412)
print(frequency8)

# Define the survey design
design8 <- svydesign(id = ~1, weights = ~stateindividualweight, data = current_scenario_male)

# Create a weighted frequency distribution table
svytable_design8 <- svytable(~we412, design = design8)
print(svytable_design8)

# Proportion table from the weighted frequency distribution
weighted_proportion_table8 <- prop.table(svytable_design8) * 100  
print(round(weighted_proportion_table8, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df8 <- as.data.frame(weighted_proportion_table8)

```


*(ii) Female*

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search3 <- sum(is.na(current_scenario_female$we412))

# Print the result
print(num_NA_job_search3)
```


```{r}
current_scenario_female <- current_scenario_female %>%
  mutate(we412 = ifelse(is.na(we412), "NA", we412),
         we412 = ifelse(we412 %in% c("1 Currently receiving", "2 Expected to receive in future"), 
                        "Currently receiving or expected to receive", we412))


# Create the frequency distribution table
frequency8a <- table(current_scenario_female$we412)
print(frequency8a)

# Define the survey design
design8a <- svydesign(id = ~1, weights = ~stateindividualweight, data = current_scenario_female)

# Create a weighted frequency distribution table
svytable_design8a <- svytable(~we412, design = design8a)
print(svytable_design8a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table8a <- prop.table(svytable_design8a) * 100  
print(round(weighted_proportion_table8a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df8a <- as.data.frame(weighted_proportion_table8a)
```


**III. Financial Security - Wages/Salary**

*(i) Male*

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search4 <- sum(is.na(labour_force_male$we014))

# Print the result
print(num_NA_job_search4)
```


```{r}
# Create the frequency distribution table
frequency9 <- table(labour_force_male$we014)
print(frequency9)

# Define the survey design
design9 <- svydesign(id = ~1, weights = ~stateindividualweight, data = labour_force_male)

# Create a weighted frequency distribution table
svytable_design9 <- svytable(~we014, design = design9)
print(svytable_design9)

# Proportion table from the weighted frequency distribution
weighted_proportion_table9 <- prop.table(svytable_design9) * 100  
print(round(weighted_proportion_table9, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df9 <- as.data.frame(weighted_proportion_table9)
```


*(ii) Female*

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search4 <- sum(is.na(labour_force_female$we014))

# Print the result
print(num_NA_job_search4)
```


```{r}
# Create the frequency distribution table
frequency9a <- table(labour_force_female$we014)
print(frequency9a)

# Define the survey design
design9a <- svydesign(id = ~1, weights = ~stateindividualweight, data = labour_force_female)

# Create a weighted frequency distribution table
svytable_design9a <- svytable(~we014, design = design9a)
print(svytable_design9a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table9a <- prop.table(svytable_design9a) * 100  
print(round(weighted_proportion_table9a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df9a <- as.data.frame(weighted_proportion_table9a)
```




**IV. Financial Security - Help from Family members**

*(i) Male*

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search5 <- sum(is.na(current_scenario_male$fs401))

# Print the result
print(num_NA_job_search5)
```


```{r}
# Create the frequency distribution table
frequency10 <- table(current_scenario_male$fs401)
print(frequency10)

# Proportion table
proportion_table10 <- prop.table(frequency10) * 100 
print(round(proportion_table10, digits=2))

# Define the survey design
design10 <- svydesign(id = ~1, weights = ~stateindividualweight, data = current_scenario_male)

# Create a weighted frequency distribution table
svytable_design10 <- svytable(~fs401, design = design10)
print(svytable_design10)

# Proportion table from the weighted frequency distribution
weighted_proportion_table10 <- prop.table(svytable_design10) * 100  
print(round(weighted_proportion_table10, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df10 <- as.data.frame(weighted_proportion_table10)

```



*(ii) Female*

*Counting NA data*
```{r}
# Assuming final_data_No_temp is your dataset
num_NA_job_search5 <- sum(is.na(current_scenario_female$fs401))

# Print the result
print(num_NA_job_search5)
```


```{r}
# Create the frequency distribution table
frequency10a <- table(current_scenario_female$fs401)
print(frequency10a)

# Proportion table
proportion_table10a <- prop.table(frequency10a) * 100 
print(round(proportion_table10a, digits=2))

# Define the survey design
design10a <- svydesign(id = ~1, weights = ~stateindividualweight, data = current_scenario_female)

# Create a weighted frequency distribution table
svytable_design10a <- svytable(~fs401, design = design10a)
print(svytable_design10a)

# Proportion table from the weighted frequency distribution
weighted_proportion_table10a <- prop.table(svytable_design10a) * 100  
print(round(weighted_proportion_table10a, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df10a <- as.data.frame(weighted_proportion_table10a)
```
