---
title: "Untitled"
author: "Mizza"
date: "2024-06-24"
output: html_document
---

```{r}
#| label: setup
#| warning: false
#| echo: false

library(ggplot2)
library(readxl)
library(dplyr)
library(tidyverse)
library(tidyr)
library(survey)
library(ggsankey)

Household <- read_excel("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/2_LASI_W1_Household_v4 1.xlsx")
Individual <- read_excel("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/3_LASI_W1_Individual_data 1.xlsx")
merged_data <- merge (Individual, Household, by = "hhid", all = TRUE)
roster <- read_excel ("C:/Users/mizza/OneDrive/Desktop/CMD/2. LASI/1_LASI_W1_HH_roster 1.xlsx")
final_data <- merge (merged_data, roster, by = "hhid", all = TRUE)
```


**DATA OF VULNERABLE GROUP - SENIOR CITIZENS**

```{r}
final_data <- final_data%>%
  rename(Age = dm005)
```

```{r}

##TO APPLY AGE FILTER##
create_age_category <- function(Age) {
  if (is.na(Age)) {
    return(NA)
  }
  
  if (Age >= 60 & Age <= 69) {
    return("Young Old")
  } else if (Age >= 70 & Age <= 79) {
    return("Old")
  } else if (Age >= 80) {
    return("Very Old")
  } else {
    return(NA) 
  }
}
final_data$AgeCategory <- sapply(final_data$Age, create_age_category)

final_data <- final_data[final_data$AgeCategory %in% c("Young Old", "Old", "Very Old"), ]
```

**EDUCATION BUCKET**

```{r}
final_data <- final_data %>%
  mutate(Education_level = case_when(
    dm006 == "2 No" ~ "Uneducated",
    dm008 %in% c("1 Less than Primary (Standard 1-4)", 
                 "2 Primary Completed (Standard 5-7)", 
                 "3 Middle Completed (Standard 8- 9)") ~ "Primary School",
    dm008 == "4 Secondary School/Matriculation completed" ~ "Secondary School",
    dm008 %in% c("5 Higher Secondary/Intermediate/Senior Secondary completed", 
                 "6 Diploma and certificate holders") ~ "Senior Secondary School",
    dm008 %in% c("7 Graduate degree (B.A., B.Sc., B. Com.) completed", 
                 "8 Post-graduate degree or (M.A., M.Sc., M. Com.) above (M.Phil, Ph.D., Post-Doc) completed", 
                 "9 Professional course/degree (B.Ed, BE, B.Tech, MBBS, BHMS, BAMS, B.Pharm, BCS, BCA, BBA, LLB, BVSc., B. Arch, M.Ed, ME, M.Tech, MD, M.Pharm, MCS, MCA, MBA,LLM, MVSc., M. Arch, MS, CA, CS, CWA)Completed") ~ "Tertiary Education",
    TRUE ~ "Other"
  ))
```

```{r}
final_data <- final_data %>%
  rename(Gender = dm003)
```



**CURRENT EMPLOYMENT SCENARIO**

```{r}
final_data<-final_data%>%
  rename(Employed = we004)
```

```{r}

# Replace NA values in the Employed column with "Never worked"
final_data$Employed[is.na(final_data$Employed)] <- "Never worked"


# Create the frequency distribution table
frequency5 <- table(final_data$Employed)
print(frequency5)
 
# Define the survey design
design5 <- svydesign(id = ~1, weights = ~stateindividualweight, data = final_data)

# Create a weighted frequency distribution table
svytable_design5 <- svytable(~Employed, design = design5)
print(svytable_design5)

# Proportion table from the weighted frequency distribution
weighted_proportion_table5 <- prop.table(svytable_design5) * 100  
print(round(weighted_proportion_table5, digits=2))

# Convert weighted_proportion_table to a data frame
weighted_proportion_df5 <- as.data.frame(weighted_proportion_table5)
```


```{r}
final_data <- final_data %>%
  mutate(
    Employed = as.factor(Employed),
    dm013 = as.factor(dm013),
    Gender = as.factor(Gender),
    Age = as.numeric(Age),
    dm021 = as.factor(dm021)
  ) %>%
  drop_na(Employed, dm013, Gender, Age, dm021)

# Create separate variables for each condition
final_data <- final_data %>%
  mutate(
    Scheduled_Caste = ifelse(dm013 == "1 Scheduled Caste", "Yes", "No"),
    Scheduled_Tribe = ifelse(dm013 == "2 Scheduled Tribe", "Yes", "No"),
    Old_Female = ifelse(Gender == "2 Female" & Age >= 80, "Yes", "No"),
    Widowed = ifelse(dm021 == "2 Widowed", "Yes", "No")
  )

# Perform chi-squared tests for each condition

# Scheduled Caste
table_scheduled_caste <- table(final_data$Employed, final_data$Scheduled_Caste)
chi_squared_scheduled_caste <- chisq.test(table_scheduled_caste)
chi_squared_scheduled_caste

# Scheduled Tribe
table_scheduled_tribe <- table(final_data$Employed, final_data$Scheduled_Tribe)
chi_squared_scheduled_tribe <- chisq.test(table_scheduled_tribe)
chi_squared_scheduled_tribe

# Old Female
table_old_female <- table(final_data$Employed, final_data$Old_Female)
chi_squared_old_female <- chisq.test(table_old_female)
chi_squared_old_female

# Widowed
table_widowed <- table(final_data$Employed, final_data$Widowed)
chi_squared_widowed <- chisq.test(table_widowed)
chi_squared_widowed
```

*i.e.., statistically significant*




*Since widowed and old female has very few sample observations it is better to use fishers test*
```{r}
final_data <- final_data %>%
  mutate(
    Decision = as.factor(Decision),
    Old_Female = as.factor(ifelse(dm003 == "2 Female" & Age >= 80, "Yes", "No")),
    Widowed = as.factor(ifelse(dm021 == "2 Widowed", "Yes", "No"))
  ) %>%
  drop_na(Decision, Old_Female, Widowed)

# Create contingency tables
table_old_female <- table(final_data$Decision, final_data$Old_Female)
table_widowed <- table(final_data$Decision, final_data$Widowed)

# Perform Fisher's Exact Test for Old Female
fisher_test_old_female <- fisher.test(table_old_female)
fisher_test_old_female

# Perform Fisher's Exact Test for Widowed
fisher_test_widowed <- fisher.test(table_widowed)
fisher_test_widowed
```

*i.e.., no significant association*



*Since widowed has very few sample observations it is better to use fishers test*
```{r}
labour_force <- labour_force %>%
  mutate(
    Occupation = as.factor(Occupation),
    Widowed = as.factor(ifelse(dm021 == "2 Widowed", "Yes", "No"))
  ) %>%
  drop_na(Occupation, Widowed)

# Create contingency tables
table_widowed <- table(labour_force$Occupation, labour_force$Widowed)

# Perform Fisher's Exact Test for Widowed
fisher_test_widowed <- fisher.test(table_widowed)
fisher_test_widowed
```

*i.e.., no significant association in widowed*


*Since old female has very few sample observations it is better to use fishers test*
```{r}
current_scenario <- current_scenario %>%
  mutate(
    we412 = as.factor(we412),
   Old_Female= as.factor(ifelse(dm003 == "2 Female" & Age >= 80, "Yes", "No"))
  ) %>%
  drop_na(we412, Old_Female)

# Create contingency tables
table_old_female <- table(current_scenario$we412, current_scenario$Old_Female)

# Perform Fisher's Exact Test for Old Female
fisher_test_old_female <- fisher.test(table_old_female)
fisher_test_old_female
```

